---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nhdplusVAA

<!-- badges: start -->
<!-- badges: end -->

`nhdplusVAA` allows researchers to use the NHD Attribute Data without the heavy geometry files.

## Installation 

You can install the development version with:

``` r
# install.packages("remotes")
remotes::install_github("mikejohnson51/nhdplusVAA")
```

## Example

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(nhdplusVAA)
```

If this is your first time using `nhdplusVAA` you'll need to download the archived data. This download goes into a local cache directory.

```{r, eval = FALSE}
download_vaa()
```

All internal functions will check if the data is local but you can check yourself too:
```{r}
check_vaa()
```

Ok! We have the data, lets see whats available in it:

```{r}
get_vaa_names()
```

And lets actually query the attribute data, for example lets get slope and slope length and use it to determine a mean slope:

```{r}
system.time({
x = get_vaa(c("slope", "lengthkm" , 'slopelenkm')) %>% 
  mutate(meanS = (slope*slopelenkm) / lengthkm)
})
```

```{r}
head(x)

dim(x)
```

